---
title: "Three solutions to a knapsack problem"
author: "Torrin Danner, Joshua Hudson, Sascha Schmalz, and Nikolajs Prihodko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Knapsack package

This package is designed to study the effects of algorithms with different complexity. 

## How to install and load

### Install 

To install the package [devtools](https://cran.r-project.org/web/packages/devtools/index.html) should be present on your machine. If you are using [RStudio](https://www.rstudio.com/), you can just run the following command
```{r, eval = FALSE}
install.packages("devtools")
```
If you are using plain R or another development environment, please refer to the package documentation for information on how to install it.

After the installation of `deevtools`, we can simply run the following command in the RStudio console
```{r, eval = FALSE}
devtools::install_github(repo = "Rchieve/732A94_Lab6", 
                         build_vignette = TRUE)
```

### Load

After the installation is successful, we want to load the package using

```{r}
library(Knapsack)
```

or access function directly, using `Knapsack::<function_name>`.


## Workflow

### Knapsack

This is where we talk about what steps to do things in 

```{r}
here<-("is where we give an example")
```

To check whether we have passed the correct address, we might want print the object:
```{r}
print(here)
```

Second, we use `another` function
```{r}
alsohere <- another(here)
```

This returns a `different` object.
You could also print using the R console./
```{r, eval = FALSE}
another
```

We can here talk about the results and varying times it takes to run each algorithm.