---
title: "Three solutions to a knapsack problem"
author: "Torrin Danner, Joshua Hudson, Sascha Schmalz, and Nikolajs Prihodko"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Knapsack package

This package is designed to study the effects of three algorithms with different complexity. The problem is given as a knapsack that has a maximum weight it can carry. Given a set of objects with varying values and weights, what is the optimal combination of items to give the greatest value in the knapsack? This is answered using three different methods, brute force, dynamic and greedy heuristic.

## How to install and load

### Install 

To install the package [devtools](https://cran.r-project.org/web/packages/devtools/index.html) should be present on your machine. If you are using [RStudio](https://www.rstudio.com/), you can just run the following command
```{r, eval = FALSE}
install.packages("devtools")
```
If you are using plain R or another development environment, please refer to the package documentation for information on how to install it.

After the installation of `deevtools`, we can simply run the following command in the RStudio console
```{r, eval = FALSE}
devtools::install_github(repo = "Rchieve/732A94_Lab6", 
                         build_vignette = TRUE)
```

### Load

After the installation is successful, we want to load the package using

```{r}
library(Knapsack)
```

or access function directly, using `Knapsack::<function_name>`.


## Workflow

### Knapsack

The first step is to create a list of items with values and weights.  It is possible to use the built-in  `genKnapsack`  function:

```{r}
generated_knapsack<-genKnapsack(200)
```

Alternatively, one may manually create a list of items in the following manner:
```{r}
set.seed(42)
n <- 2000
knapsack_objects <-
data.frame(
w=sample(1:4000, size = n, replace = TRUE),
v=runif(n = n, 0, 10000)
)
```

This can then be used within the other functions.

###Brute Force

The `knapsack_brute_force` function analyzes every possible combination and therefore always returns the maximum possible value for the knapsack. However, this thoroughness makes the algorithm inefficient.

The `knapsack_brute_force` function is used by inputting the list of objects and the total weight the knapsack can carry. It can be seen in the following example:
```{r}
knapsack_brute_force(x = knapsack_objects[1:8,], W = 3500)
```

This returns two `list` objects.  The first is composed of a `double` of the maximum discovered value of the knapsack.  The second is composed of one or more `double` that represent the items included in the knapsack.

###Dynamic Programming

The `knapsack_dynamic` assumes discrete values for the item weights. It iterates over all possible values of \code{w} (weight). It returns the same results as `knapsack_brute_force` but is more efficient.

The `knapsack_dynamic` function is used by inputting the list of objects and the total weight the knapsack can carry. It can be seen in the following example:
```{r}
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```

This returns two `list` objects.  The first is composed of a `double` of the maximum discovered value of the knapsack.  The second is composed of one or more `double` that represent the items included in the knapsack.

###Greedy Heuristic

The `knapsack_greedy` function uses an approximation that will not necessarily give the exact result, but will drastically reduce the processing time and load as compared to the previous methods.

The `knapsack_brute_force` function is used by inputting the list of objects and the total weight the knapsack can carry. It can be seen in the following example:
```{r}
knapsack_greedy(x = knapsack_objects[1:800,], W = 3500)
```

This returns two `list` objects.  The first is composed of a `double` of the maximum discovered value of the knapsack.  The second is composed of one or more `double` that represent the items included in the knapsack.

